Untitled

### 2025-02-27 script/r/draft.Rmd
add adm harmonization for geo controls

```{r}
data_final_r <- readRDS("data/data_rds/data_final_r.rds")

desert_adm1 <- readRDS("data/data_rds/geo_ctrl/desert_adm1.rds")
desert_adm2 <- readRDS("data/data_rds/geo_ctrl/desert_adm2.rds")

@@

@@

saveRDS(data_final_r, file="data/data_rds/data_27_05_25.rds")

write_dta(data_final_r, "data/data_dta/data_27_05_25.dta")
```

>>>>

```{r}
desert_adm1 <- readRDS("data/data_rds/geo_ctrl/desert_adm1.rds")
desert_adm2 <- readRDS("data/data_rds/geo_ctrl/desert_adm2.rds")

@@

data_final_r <- readRDS("data/data_rds/data_final_r.rds")

@@

countries_adm1 <- c("GHA","KEN","MOZ", "MWI","NGA","TZA","UGA","ZMB", "ZWE")
countries_adm2 <- c("BEN", "BFA", "BWA", "CIV", "CMR", "GIN", "LBR", "MLI", "NAM", "NER", "SLE")

data_final_r %<>%
mutate(desert_region = case_when(
    iso %in% countries_adm1 ~ desert_adm1,
    iso %in% countries_adm2 ~ desert_adm2, 
    TRUE ~ NA_integer_
  ))%>%
mutate(elevation_region = case_when(
    iso %in% countries_adm1 ~ elevation_adm1,
    iso %in% countries_adm2 ~ elevation_adm2, 
    TRUE ~ NA_integer_
  ))%>%
mutate(mountain_region = case_when(
    iso %in% countries_adm1 ~ mountain_adm1,
    iso %in% countries_adm2 ~ mountain_adm2, 
    TRUE ~ NA_integer_
  ))%>%
mutate(precipitation_region = case_when(
    iso %in% countries_adm1 ~ precipitation_adm1,
    iso %in% countries_adm2 ~ precipitation_adm2, 
    TRUE ~ NA_integer_
  ))%>%
mutate(temp_max_region = case_when(
    iso %in% countries_adm1 ~ temp_max_adm1,
    iso %in% countries_adm2 ~ temp_max_adm2, 
    TRUE ~ NA_integer_
  ))%>%
mutate(temp_min_region = case_when(
    iso %in% countries_adm1 ~ temp_min_adm1,
    iso %in% countries_adm2 ~ temp_min_adm2, 
    TRUE ~ NA_integer_
  ))%>%
mutate(temp_mean_region = case_when(
    iso %in% countries_adm1 ~ temp_mean_adm1,
    iso %in% countries_adm2 ~ temp_mean_adm2, 
    TRUE ~ NA_integer_
  ))

saveRDS(data_final_r, file="data/data_rds/data_27_02_25.rds")

write_dta(data_final_r, "data/data_dta/data_27_02_25.dta")
```
